### 2021-02-14 results.tex
add a venn-diagram for the first study

As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default configuration. After that, we executed the analysis again though disabling the DroidFax static analysis algorithm, so that we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes. Table~\ref{tab:fs} summarizes the results of th execution. The columns Exec. (I) and Exec. (II) 
show the number of malwares identified when executing each tool (I) with the
support of the DroidFax static analysis algorithms and (II) withouth the support
of DroidFax static analysis algorithms. The Improvement column shows the impact
(in percentage) of DroidFax static analysis algorithms in the results.
In the previous work~\cite{}, the authors do not present a
discussion about the influence of DroidFax in the results, even
though here we report that this difference is in the
range from 23.94\% (Monkey) to 69.39\% (Humanoid)---discarding our
\joke tool for wich DroidFax improves its performance in 100\% (as expected).
Next we discuss the result of each individual test generation tool.

\begin{table}[ht]
  \caption{Summary of the results of the first study. }
  \centering
  \begin{small}
 \begin{tabular}{lrrr}
   \toprule
   Tool & Exec. (I) & Exec. (II) & Improvement (\%) \\   \midrule
  Monkey &  71 &  54 & 23.94 \\ 
  Droidmate &  64 &  48 & 25.00 \\ 
  Droidbot &  68 &  54 & 20.59 \\ 
  Humanoid &  49 &  15 & 69.39 \\ 
  \joke &  42 &   0 & 100.00 \\ 
 \bottomrule
 \end{tabular}
 \end{small}
 \label{tab:fs}
\end{table}

\subsubsection*{Monkey} sandbox for the first execution (Exec. (I)) detected more apps with malicious behavior than any other tool considered in our study (71 out of the 96 pairs of Android apps). Contrasting, in the original study, Monkey got the third-best performance, detecting 48 malwares within the 102 pairs (47.05\%). This difference might be due to the Monkey randomic strategy for test case generation. \rb{I am not convinced that the other tools do not employ any randomness.} For our second execution (Exec. (II)), there is a reduction of 23.94\% in the Monkey's performance, totaling 54 malware detected---which matches the performance of Droidbot for Exec. (II). \rb{Considering only one run for each configuration, that is Exec. (I) and Exec. (II), we cannot assure that the difference is due to disabling the DroidFax static analysis algorithms.}

\subsubsection*{Droidbot} in the first execution (Exec. (I)) its resulting sandbox detected a total of 68 malware among $96$ pairs analyzed (70.83\%). Interesting, this is the same performance of the original study---although the original study analyzed $102$ pairs of Android apps. Also, in the original study, Droidbot was the test case generation tool whose resulting sandbox detected the largest number of malicious apps. However, in our second execution (Exec. (II)), its performance decreased in 20.58 \%. \rb{Not sure if the following sentence is right.} Despite this reduction, it achieved the largest number of malicious apps detected in the second execution.

\subsubsection*{Droimate} in the first execution led to a sandbox that detected 64 apps with malicious behavior (66.66\%). Contrasting, in the original study Droidmate detected 54 among 102 (52.94\%). A possible explanation for this difference is that here we use the more recent version of Droidmate. In the second execution, without the DroidFax static analysis algorithms, the resulting sandbox's performance drops by 25\%, being able to detect 48 out of the 96 pairs of Android apps.

\subsubsection*{Humanoid} presented the worse performance, even though a previous
work~\cite{DBLP:conf/kbse/LiY0C19} shows that it presents the highest lines coverage in comparison to Monkey, DroidBot, and DroidMate. In the first execution (Exec. (I)), the resulting Humanoid sandbox identified 49 malwares in our dataset (51.04\%). Since Bao et al. did not explored Humanoid in their study, we do not hava a baseline for comparison. Regarding the second execution, without static analysis, Humanoid was the most affected by disabling the DroidFax static analysis algorithm, losing 69.38\% of its effectiveness, and being able to detect just 15 malwares.

\subsubsection*{\joke} is our fake test case generation tool that we use to help us understand the performance of the DroidFax static analysis algorithm for mining sandboxes. We integrated \joke into the DroidXP benchmark as an additional test generation tool that does not run the Android apps during the benchmark execution. As a result, the analysis using \joke reveals the performance of DroidFax static analysis algorithms only. For the first execution, with the DroidFax static algorithms enabled, even though \joke does not execute the Android apps, its resulting sandbox detected 43.75\% of the malwares. For the second execution, that is, disabling the DroidFax static analysis algorithm, the resulting \joke sandbox was unable to detect any malware. This result was expected, since \joke does not analyse the Android apps during the benchmark execution.

Ignoring the \joke tool, our study show that 51.04\%-73.95\% of the malicious apps investigatedin our study can be detected using the sandboxes constructed running the test case generation tools with the support of DroidFax static analysis algorithms. Besides that, in the first execution none of the resulting sandboxes could detect 19 malwares in our dataset (19.79\%). According to the Euphony tool~\cite{hurier2017euphony}, 13 of these 19 malwares are adwares, three are trojans, two are PUP (Potentially Unwanted Program), and one is an exploit.

\rb{This is an interesting point to present the details of two or three malwares in this set of 19 malwares that had not been detected by any tool.}

\begin{finding}
Based on these results, we provide evidence that, although static analysis Droidfax, do not affect detection malware at 19 specific pair apps, its absence impact on sandboxes performance, impairing the accuracy of all of them.
\end{finding}

@@

To complement our initial survey, we performed our second study focusing just on static analysis, but this time, using an algorithm different from the first study, performed by Droidfax. This time, we used tainted analysis algorithms, using FlowDroid tool, that tracking how private information flows through the apps, and if it is leaked in an unwanted way. The results presents were obtained through the analysis of the same data set of the previous study, that is, on the same 96 pairs apps (B/M).

The first results show that with tainted analysis, we had an analysis processing cost of 32.08 seconds per app pair on average, totaling a processing time of 52 minutes to analyze all the pairs. The processing time depends on the size of the app, and the pair that took the fastest time analyzed in 3 seconds and the longest 437 seconds. Regarding the accuracy of tainted analysis algorithms our study also shows that it was responsible to detect 58 among 96 pair apps (60,42\%), a quantity higher than presented by static analysis algorithms Droidfax, suggested by Joke, our fake test case generation tool, that detected 43.75\% of malware as showed at our first study.

Considering the static analysis provided by Droidfax, and Flowdroid, our results showed that both were able to detect 33 pairs in common (34.37\%), and there were 29 pairs that both were not able to detect (30.20\%). We also realized that just 9 pairs were detected by Droidfax and do not by FlowDroid, while 25 pairs were detected by FlowDroid, and do not by Droidfax, evincing a better accuracy of tainted analysis algorithm. Table \ref{tab:comparison} compile the results of this comparison.

@@

Detected by  & Malwares detected & \%   \\ 
(Droidfax/Flowdroid) & (Among 96 pair) & \\ \midrule
Both tools & 33 & 34.37\%  \\
Just Droidfax & 9 &  \\
Just Flowdroid & 25 &  \\
None & 29 & 30.20\% \\\midrule

\multicolumn{1}{r}{Total} &   96 \\ \bottomrule
\end{tabular} 
\caption{Comparison between Droidfax and Flowdroid algorithms}
\label{tab:comparison}
\end{table}

Furthermore, we can highlight that among 19 pair apps that at first study, were not detected by the sandboxes constructed by test generation tool, and static analysis Droidfax miner, 4 were detected by Flowdroid; P35, P38, P56, and P94, therefore exposing better accuracy of the tainted analysis algorithms. Among these 4 pairs detected, 2 were trojans, 1 was the exploit, and 1 was adware.

@@

First we find that static analysis summaries had impact in the Bao et al. study. It was responsible for improving the results of the tools by 47.78\% than its executions alone, answering our first research question (RQ1). Second, Table \ref{tab:malwareWithout} summarizes our findings addressing the second research question (RQ2). We realized that disregarding the static analysis algorithms, and discarding Joke tool, among the tools analyzed in your study, Humanoid had the biggest performance drop, and the least affected was Droidbot, proving be the tool with better effective performance, in terms of the number of detected malware. Finally, we answered our last research question (RQ3) when we leverage sandboxes, complementing the dynamic analysis provided by test generation tool with tainted analysis algorithms. Our experiment highlight that 69.79\%-81.25\% of malware in dataset can be now uncovered by the complement of tainted analysis algorithms, evidencing that 
sandboxes can be further boosted when coupled with new static analysis techniques. We found that the number of identified malicious apps detected is increased for all cases, achieving at the best case, 81.25\% with Monkey, a better performance than all five tools explored at Bao et al., even when they combined all the tools together at theirs work 75.49\%. Table \ref{tab:tanted} display the increase of all tools explored at our research.

\begin{table}[ht]
\centering
\begin{tabular}{lccc}\toprule
 Test Generation & FlowDroid & Total & \%\\
 Tool & Increase  &  & \\ \midrule
 Monkey & 7 & 78 & 81.25\\
 Droidmate & 10 &  74 & 77.08 \\
 Humanoid & 20 & 69 & 71.87  \\
 Joke & 25 & 67 & 69.79 \\
 Droidbot & 9 & 77 & 80.20  \\\midrule

>>>>

As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default configuration. After that, we executed the analysis again though disabling the DroidFax static analysis algorithm, so that we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes. Table~\ref{tab:fs} summarizes the results of the execution. The columns Exec. (I) and Exec. (II) 
show the number of malwares identified when executing each tool (I) with the
support of the DroidFax static analysis algorithms and (II) without the support
of DroidFax static analysis algorithms. The Improvement column shows the impact
(in percentage) of DroidFax static analysis algorithms in the results.
In the previous work~\cite{}, the authors do not present a
discussion about the influence of DroidFax in the results, even
though here we report that this difference is in the
range from 23.94\% (Monkey) to 69.39\% (Humanoid)---discarding our
\joke tool for which DroidFax improves its performance in 100\% (as expected).
Next we discuss the result of each individual test generation tool.

\begin{table}[ht]
  \caption{Summary of the results of the first study. }
  \centering
  \begin{small}
 \begin{tabular}{lrrr}
   \toprule
   Tool & Exec. (I) & Exec. (II) & Improvement (\%) \\   \midrule
  Monkey &  71 &  54 & 23.94 \\ 
  DroidMate &  64 &  48 & 25.00 \\ 
  DroidBot &  68 &  54 & 20.59 \\ 
  Humanoid &  49 &  15 & 69.39 \\ 
  \joke &  42 &   0 & 100.00 \\ 
 \bottomrule
 \end{tabular}
 \end{small}
 \label{tab:fs}
\end{table}

\subsubsection*{Monkey} sandbox for the first execution (Exec. (I)) detected more apps with malicious behavior than any other tool considered in our study (71 out of the 96 pairs of Android apps). Contrasting, in the original study, Monkey got the third-best performance, detecting 48 malwares within the 102 pairs (47.05\%). This difference might be due to the Monkey randomly strategy for test case generation. \rb{I am not convinced that the other tools do not employ any randomness.} For our second execution (Exec. (II)), there is a reduction of 23.94\% in the Monkey's performance, totaling 54 malware detected---which matches the performance of DroidBot for Exec. (II). \rb{Considering only one run for each configuration, that is Exec. (I) and Exec. (II), we cannot assure that the difference is due to disabling the DroidFax static analysis algorithms.}

\subsubsection*{DroidBot} in the first execution (Exec. (I)) its resulting sandbox detected a total of 68 malware among $96$ pairs analyzed (70.83\%). Interesting, this is the same performance of the original study---although the original study analyzed $102$ pairs of Android apps. Also, in the original study, DroidBot was the test case generation tool whose resulting sandbox detected the largest number of malicious apps. However, in our second execution (Exec. (II)), its performance decreased in 20.58 \%. \rb{Not sure if the following sentence is right.} Despite this reduction, it achieved the largest number of malicious apps detected in the second execution.

\subsubsection*{DroidMate} in the first execution led to a sandbox that detected 64 apps with malicious behavior (66.66\%). Contrasting, in the original study DroidMate detected 54 among 102 (52.94\%). A possible explanation for this difference is that here we use the more recent version of DroidMate. In the second execution, without the DroidFax static analysis algorithms, the resulting sandbox's performance drops by 25\%, being able to detect 48 out of the 96 pairs of Android apps.

\subsubsection*{Humanoid} presented the worse performance, even though a previous
work~\cite{DBLP:conf/kbse/LiY0C19} shows that it presents the highest lines coverage in comparison to Monkey, DroidBot, and DroidMate. In the first execution (Exec. (I)), the resulting Humanoid sandbox identified 49 malwares in our dataset (51.04\%). Since Bao et al. did not explored Humanoid in their study, we do not have a baseline for comparison. Regarding the second execution, without static analysis, Humanoid was the most affected by disabling the DroidFax static analysis algorithm, losing 69.38\% of its effectiveness, and being able to detect just 15 malwares.

\subsubsection*{\joke} is our fake test case generation tool that we use to help us understand the performance of the DroidFax static analysis algorithm for mining sandboxes. We integrated \joke into the DroidXP benchmark as an additional test generation tool that does not run the Android apps during the benchmark execution. As a result, the analysis using \joke reveals the performance of DroidFax static analysis algorithms only. For the first execution, with the DroidFax static algorithms enabled, even though \joke does not execute the Android apps, its resulting sandbox detected 43.75\% of the malwares. For the second execution, that is, disabling the DroidFax static analysis algorithm, the resulting \joke sandbox was unable to detect any malware. This result was expected, since \joke does not analyze the Android apps during the benchmark execution.

\begin{finding}
  Integrating the dynamic analysis tools
  with the DroidFax static analysis algorithms
  improves substantially the performance
  of the resulting Android sandboxes for
  detecting malicious behavior. 
\end{finding}

The Venn-diagram of Figure~\ref{fig:venn-plot1}
summarizes how the tools can complement each other.
Note in the diagram that 47 malwares have been detected by all sandboxes generated in the first execution (with the DroidFax static analysis algorithms), out of the 77 identified by at least one sandbox. In addition, the DroidBot sandbox did not detect any malware that had not been detected by the other tools. Differently, the Monkey's sandbox detected five malwares that had not been detected by any other sandbox, DroidBot sandbox detected four malwares that had not been detected by any other sandbox, and Humanoid detected one malware that had not been detected by any other sandbox. Contrasting with the Bao et al. work~\cite{DBLP:conf/wcre/BaoLL18},
our results suggest that using DroidBot in combination with Monkey, DroidMate, and Humanoid does not improve the general performance of an integrated environment for mining
Android sandboxes.

\begin{finding}
  Our results suggest that one might benefit from using  an integrated
  environment that combines Monkey, DroidMate, and Humanoid to
  mine Android sandboxes. Introducing the DroidBot 
  tool does not improve the results.
\end{finding}

\begin{figure}[htb]
  \centering{
  \includegraphics[trim=60 20 0 50,scale=0.7]{images/venn-plot-1.pdf}}
  \caption{Venn Diagram highlighting how the sandboxes from the tools can
    complement each other.}
  \label{fig:venn-plot1}
\end{figure}

Altogether, ignoring the \joke tool, our study reveals that from 51.04\% (Humanoid)
to 73.95\% (Monkey) of the malicious apps investigated in our study can be
detected using the sandboxes generated after running the test case tools with the support of DroidFax static analysis algorithms. Besides that, in the first execution, none of the resulting sandboxes could detect 19 malwares in our dataset (19.79\%). According to the Euphony tool~\cite{hurier2017euphony}, 13 of these 19 malwares are \emph{adwares}, three are \emph{trojans}, two are PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}. \rb{In what follows we present some characteristics of malwares that had not been detected by the sandboxes.}

\rb{This is an interesting place to present the details of two or three malwares in this set of 19 malwares that had not been detected by any tool. I think Thales could work on this, since he has helped Handrick to dissect the malwares.}

@@

In this second study we used a tainted analysis approach to mine differences between the benign and malicious versions of each of the 96 Android apps in our dataset. To this end we leverage the FlowDroid tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms. Regarding accuracy, the tainted analysis approach detected 58 out of the 96 pairs in our dataset (60,42\%), that is, the FlowDroid approach leads to a better performance than any sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms).

\begin{finding}
  The performance of FlowDroid to identify malicious behavior
  using our approach is superior than the performance of the
  mining sandbox approach supported by dynamic analysis only---without
  the DroidFax static analysis algorithms.
\end{finding}

Additionally, we investigate if we could benefit from combining
the results from FlowDroid and DroidFax. Figure~\ref{}
shows the results.
Considering the static analysis provided by DroidFax and FlowDroid, our results showed that both were able to detect 33 pairs in common (34.37\%), and there were 29 pairs that both were not able to detect (30.20\%). We also realized that just 9 pairs were detected by DroidFax and do not by FlowDroid, while 25 pairs were detected by FlowDroid, and do not by DroidFax, evincing a better accuracy of tainted analysis algorithm.

The first results show that with tainted analysis, we had an analysis processing cost of 32.08 seconds per app pair on average, totaling a processing time of 52 minutes to analyze all the pairs. The processing time depends on the size of the app, and the pair that took the fastest time analyzed in 3 seconds and the longest 437 seconds.

Table \ref{tab:comparison} compile the results of this comparison.

@@

Detected by  & Malwares detected & \%   \\ 
(DroidFax/FlowDroid) & (Among 96 pair) & \\ \midrule
Both tools & 33 & 34.37\%  \\
Just DroidFax & 9 &  \\
Just FlowDroid & 25 &  \\
None & 29 & 30.20\% \\\midrule

\multicolumn{1}{r}{Total} &   96 \\ \bottomrule
\end{tabular} 
\caption{Comparison between DroidFax and FlowDroid algorithms}
\label{tab:comparison}
\end{table}

Furthermore, we can highlight that among 19 pair apps that at first study, were not detected by the sandboxes constructed by test generation tool, and static analysis DroidFax miner, 4 were detected by FlowDroid; P35, P38, P56, and P94, therefore exposing better accuracy of the tainted analysis algorithms. Among these 4 pairs detected, 2 were trojans, 1 was the exploit, and 1 was adware.

@@

First we find that static analysis summaries had impact in the Bao et al. study. It was responsible for improving the results of the tools by 47.78\% than its executions alone, answering our first research question (RQ1). Second, Table \ref{tab:malwareWithout} summarizes our findings addressing the second research question (RQ2). We realized that disregarding the static analysis algorithms, and discarding Joke tool, among the tools analyzed in your study, Humanoid had the biggest performance drop, and the least affected was DroidBot, proving be the tool with better effective performance, in terms of the number of detected malware. Finally, we answered our last research question (RQ3) when we leverage sandboxes, complementing the dynamic analysis provided by test generation tool with tainted analysis algorithms. Our experiment highlight that 69.79\%-81.25\% of malware in dataset can be now uncovered by the complement of tainted analysis algorithms, evidencing that 
sandboxes can be further boosted when coupled with new static analysis techniques. We found that the number of identified malicious apps detected is increased for all cases, achieving at the best case, 81.25\% with Monkey, a better performance than all five tools explored at Bao et al., even when they combined all the tools together at theirs work 75.49\%. Table \ref{tab:tanted} display the increase of all tools explored at our research.

\begin{table}[ht]
\centering
\begin{tabular}{lccc}\toprule
 Test Generation & FlowDroid & Total & \%\\
 Tool & Increase  &  & \\ \midrule
 Monkey & 7 & 78 & 81.25\\
 DroidMate & 10 &  74 & 77.08 \\
 Humanoid & 20 & 69 & 71.87  \\
 Joke & 25 & 67 & 69.79 \\
 DroidBot & 9 & 77 & 80.20  \\\midrule
